### 2022-07-30 paper/akweury/document.tex
update nnnn model

\section{GCNN model evaluation based on Geometry Information}
The GCNN model is the base model of the whole thesis. The architecture is described in \ref{sec:gcnn}. We use a single GCNN to estimate the surface normal based on geometry information. It uses vertex map as input to estimate the corresponding tangent surface normal map.

>>>>

\section{GCNN model based on Geometry Information}
The GCNN model is the base model of the whole thesis. The architecture is described in \ref{sec:gcnn}. We use a single GCNN to estimate the surface normal based on geometry information. It uses vertex map as input to estimate the corresponding tangent surface normal map.

\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
The Trip-Net model is the base model of the whole thesis. The architecture is described in \ref{sec:gcnn}. We use a single GCNN to estimate the surface normal based on geometry information. It uses vertex map as input to estimate the corresponding tangent surface normal map.
